\documentclass[journal,10pt]{IEEEtran}

\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{cite}
\usepackage{url}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}

\graphicspath{{figures/}{../figures/}}
\input{macros}
\input{metadata}

\begin{document}

\maketitle

\begin{abstract}
Retrieval, external memory, and evidence verification are often attached to small
language models under the assumption that more grounding will improve reliability.
That assumption ignores two coupled questions: whether a generator can use the
added evidence under a strict output contract, and whether the resulting quality
gain justifies its computational cost. We present E2AM-MemRAG, a controlled study
of generator-dependent grounding and energy-aware routing. The study constructs
800 deterministic scenario groups across eight evidence and memory tasks, freezes
grouped train/calibration/validation/test splits, and evaluates 17 pilot-retained
routes on 120 sealed-test questions. Five pinned FP16 generators are compared
directly and under an identical hybrid-retrieval, graph-memory, and deterministic
verification route. Success requires answer correctness, complete required-evidence
citations, perfect citation precision, correct abstention, parseability, and no
forbidden evidence. Generation-window selected-GPU board energy is obtained by
integrating 50-ms NVML power samples on NVIDIA T4 GPUs; CPU and whole-system energy
are outside this boundary.

Grounding was not uniformly beneficial. It changed strict success by
$-12.5$ percentage points for Qwen3-0.6B, $+23.3$ points for Granite-4.1-3B,
$+10.8$ points for SmolLM3-3B, and $+29.2$ points for Qwen3-4B. Every grounded
endpoint had a higher observed GPU-energy mean; four pairs were same-board and
the Granite-4.0-1B contrast was cross-board. The best route reached 44.2\% strict
success at 176.68 J/query. The router's validation constraints were infeasible;
a disclosed pre-test amendment froze a fail-closed threshold and prohibited a
positive routing claim. On test, the policy fell back to the same route for all
queries, obtained 0\% strict success, and saved 0 J, so the confirmatory hypothesis
failed. The result is a mechanism-level negative finding: infeasible calibration
constraints and an uninformative fail-closed rule can nullify an otherwise useful
route set, and grounding gains must be established per generator rather than assumed.
\end{abstract}

\begin{IEEEkeywords}
retrieval-augmented generation, language-model routing, Green AI, GPU energy,
long-term memory, abstention, negative results, reproducible evaluation
\end{IEEEkeywords}

\input{sections/01_introduction}
\input{sections/02_related_work}
\input{sections/03_hybridbench}
\input{sections/04_methodology}
\input{sections/05_experimental_protocol}
\input{sections/06_results}
\input{sections/07_failure_analysis}
\input{sections/08_limitations_ethics}
\input{sections/09_conclusion}

\appendices
\input{appendices/route_catalog}
\input{appendices/scoring_contract}
\input{appendices/reproducibility}
\input{appendices/scenario_effects}

\section*{Acknowledgment}
The author thanks the open-source model and tooling communities whose released
artifacts made the controlled study possible. No external sponsor influenced the
study design, analysis, or reporting.

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
