\section{Introduction}
\label{sec:introduction}

Retrieval-augmented generation (RAG) gives a language model access to evidence
that is fresher, more specific, or more auditable than its parameters alone
\cite{Lewis2020RAG}. In practice, however, ``adding RAG'' is not one intervention.
A deployed pipeline may decide whether to retrieve, choose sparse or dense search,
expand a second hop, consult long-term memory, lengthen the prompt, invoke a larger
generator, verify citations, or abstain. Each decision changes both the available
evidence and the work performed. A quality-only evaluation can therefore reward a
route that is too expensive to deploy, while a cost-only router can learn to choose
cheap routes that do not satisfy the evidence contract.

This tension is especially sharp for compact language models. Small generators are
attractive for local and resource-constrained inference, but retrieved context is
useful only if the generator can identify the relevant facts, follow the requested
schema, cite the correct evidence, and withhold unsupported answers. Imperfect or
distracting context can actively reduce answer quality
\cite{OhThorne2023DetrimentalContexts,ParkLee2024RobustRALM}. Consequently, the
effect of grounding is an interaction among the generator, retrieval mechanism,
memory organization, prompt budget, and verifier; it is not a property of the
retriever in isolation.

Efficiency introduces a second ambiguity. Prior work has argued that computational
cost should be reported alongside predictive quality
\cite{SchwartzEtAl2020GreenAI,HendersonEtAl2020EnergyReporting}, and inference itself
can be a material energy burden \cite{LuccioniEtAl2024PowerHungry}. Yet ``energy''
may refer to a GPU board, a host, an entire cluster, or a carbon estimate. This
study uses a deliberately narrow, reproducible quantity: board-power samples from
the selected NVIDIA T4 integrated over the call to \texttt{model.generate()}.
Retrieval runs on CPU and is charged to latency, not to the reported GPU-energy
quantity. We make that boundary explicit because equating GPU board energy with
whole-system energy or carbon would be scientifically incorrect.

Model routing appears to offer a natural solution. Cascades and learned routers can
trade quality against monetary or computational cost
\cite{ChenZahariaZou2024FrugalGPT,DingEtAl2024HybridLLM,OngEtAl2024RouteLLM}. For a
RAG system, however, a router must choose among composite actions rather than only
among model endpoints. Its candidate pool must also contain routes whose success is
predictable from information available at decision time. Calibration alone cannot
create such separation: a controller that predicts failure for every action can be
well calibrated but operationally useless.

We study these issues through \system, a frozen controlled experiment rather than
a claim about open-domain question answering. \bench{} contains 800 deterministic
scenario groups spanning direct copying, knowledge retrieval, personal memory,
knowledge--memory composition, temporal updates, authority conflicts, two-hop
retrieval, and deleted or missing evidence. Opaque identifiers prevent parametric
memorization of the answers. Grouped splits isolate pilot pruning, router fitting,
calibration, threshold selection, and a 120-question sealed test. A strict success
indicator requires both answer correctness and exact satisfaction of the
applicable citation, abstention, and forbidden-evidence conditions.

The experiment separates three questions. First, a controlled mechanism matrix
compares direct generation with BM25, dense, hybrid, and three memory organizations.
Second, a five-generator matched panel applies the same direct and grounded route
to Qwen3-0.6B, Granite-4.0-1B, Granite-4.1-3B, SmolLM3-3B, and
Qwen3-4B-Instruct-2507. Third, a two-stage calibrated router uses only deployable
tiny/small routes and is tested against a validation-selected fixed route. All
clean test routes cover the same 120 questions, permitting paired, scenario-cluster
bootstrap analysis.

The outcome is informative precisely because it is not a routing success. The
validation constraints were infeasible: no threshold reached the frozen 80\%
success floor while satisfying coverage and abstention bounds. Before test labels
were accessed, a documented amendment expanded the threshold grid and froze a
fail-closed threshold of one, explicitly forbidding a positive hypothesis claim.
The resulting policy selected its safe fallback, \route{A03\_tiny\_hybrid}, for all
test questions. It achieved zero strict success and reproduced the baseline's
143.16 J/query, so the predeclared energy-reduction hypothesis failed.

The matched generator panel nevertheless exposes a substantial interaction.
Grounding changed strict success by $-12.5$ \pp{} for Qwen3-0.6B,
$+23.3$ \pp{} for Granite-4.1-3B, $+10.8$ \pp{} for SmolLM3-3B, and
$+29.2$ \pp{} for Qwen3-4B. Every grounded endpoint had a higher observed
generation-window GPU-energy mean; four of the five pairs were same-board. The
small Granite-4.0-1B pair produced no
parseable outputs under the frozen prompt/runtime contract, so it is treated as a
compatibility failure rather than evidence of general model incapacity.

The paper makes five contributions:

\begin{enumerate}
    \item a deterministic benchmark that isolates retrieval, memory, temporal,
    authority, abstention, and citation requirements under grouped leakage controls;
    \item a matched five-generator design that distinguishes generator-dependent
    grounding effects from a flat model leaderboard;
    \item an explicit generation-window GPU-energy protocol with complete telemetry,
    paired latency measurement, and no carbon or whole-system extrapolation;
    \item a calibrated composite-action routing protocol with test sealing,
    abstention and coverage constraints, immutable artifacts, and fresh-root restore;
    \item a reproducible negative result identifying validation infeasibility,
    safe-route collapse, context-sensitive tiny-model behavior, a model-format
    incompatibility, and robustness floor effects.
\end{enumerate}

The central conclusion is bounded but consequential: having a useful action is not
enough if the frozen calibration constraints and decision rule cannot certify or
select it. Here, sealed-test analysis later showed that direct route A00 was both
more accurate and lower-energy than the universal fallback A03, even though no
validation threshold satisfied the predeclared 80\% success floor together with
coverage and abstention constraints. Before an energy-aware RAG controller is
optimized, each generator's ability to use the grounding contract and the
feasibility of the selection rule must be established; operational infeasibility
must remain a reportable outcome rather than an exception to suppress.
