\section{Related Work and Unresolved Gap}
\label{sec:related}

\subsection{Adaptive Retrieval and Composite Routing}

RAG couples a parametric generator to retrieved non-parametric evidence
\cite{Lewis2020RAG}. Adaptive systems subsequently made retrieval conditional:
FLARE retrieves around uncertain continuations \cite{JiangEtAl2023FLARE},
Adaptive-RAG selects among retrieval depths \cite{JeongEtAl2024AdaptiveRAG}, and
Self-RAG learns retrieval and critique decisions \cite{AsaiEtAl2024SelfRAG}.
Parallel work routes among language models to trade quality against monetary or
computational cost \cite{ChenZahariaZou2024FrugalGPT,DingEtAl2024HybridLLM,
OngEtAl2024RouteLLM}.

Our headroom statistic is not a new algorithm-selection construct. Per-instance
algorithm selection has long compared a single best solver with a label-aware
virtual best solver \cite{Rice1976AlgorithmSelection,
LindauerEtAl2019AlgorithmSelection}. In contemporary LLM routing,
LLMRouterBench explicitly treats model complementarity as the premise for routing
and measures a remaining Oracle gap \cite{LiEtAl2026LLMRouterBench}. We adapt this
established comparison to composite RAG actions scored by evidence-qualified
utility. The contribution is the integrated five-question audit---interface
compatibility, capability, complementarity, cost comparability, and constrained
selectability---and its application to immutable traces, not the subtraction of
oracle and single-best scores by itself.

Recent methods join these ideas more directly. RAGRouter conditions generator
selection on retrieved documents \cite{ZhangEtAl2025RAGRouter}; $R^3$AG separates
retrieval quality from downstream generation utility when routing retrievers
\cite{ZhaoEtAl2026R3AG}. X-Router chooses among direct, RAG, chain-of-thought, and
combined pipelines \cite{WangEtAl2026XRouter}; RouteRAG selects text or graph
evidence and reasoning actions \cite{GuoEtAl2026RouteRAG}; and RAG-on-a-Diet makes
model choices at individual reasoning hops \cite{DingZhao2026RAGDiet}. These works
establish retrieval-aware and composite-action routing as active research areas.
Accordingly, our novelty is not the existence of a RAG router or an oracle gap. We
ask whether the established complementarity diagnostic, combined with interface,
physical-cost, and validation-feasibility checks, would have rejected the action
pool before policy optimization.

\input{tables/related_work_scope}

\subsection{Context Utility and Evidence-Qualified Evaluation}

The value of retrieved context depends on model capability, task, context length,
and retrieval properties \cite{LiEtAl2025LaRA}. Irrelevant, misleading, or
internally conflicting context can impair generation
\cite{OhThorne2023DetrimentalContexts,ParkLee2024RobustRALM}, while ASTUTE RAG
explicitly targets imperfect retrieval and parametric--context conflicts
\cite{WangEtAl2025AstuteRAG}. Robustness methods such as RoseRAG and PRA-RAG address
noise or retrieval corruption with learned and provable defenses
\cite{LiuEtAl2025RoseRAG,TanEtAl2026PRARAG}. Our four corruptions are therefore a
diagnostic negative control, not a new defense or a broad adversarial-robustness
claim.

Answer accuracy alone can hide unsupported generation. KILT links answers to
provenance \cite{PetroniEtAl2021KILT}; ALCE evaluates citation correctness and
completeness \cite{GaoEtAl2023ALCE}; and GaRAGe provides grounding annotations and
deflection-oriented evaluation \cite{SorodocEtAl2025GaRAGe}. We combine answer,
exact citation, abstention, parsing, and forbidden-evidence conditions in a single
strict indicator so that a route cannot receive utility for an ungrounded correct
string. The resulting metric is intentionally operational and harsher than human
judgment; it does not establish semantic entailment.

Synthetic testbeds provide experimental control but can exaggerate context-use
patterns that do not survive realistic retrieval
\cite{HagstromEtAl2025RealityCheck}. We therefore describe \bench{} as a mechanism
identification testbed. It isolates failures under known evidence requirements; it
does not estimate open-domain QA performance.

\subsection{External Memory}

External-memory research ranges from separate long-term memory networks
\cite{WangEtAl2023LongMem} and user-history stores \cite{ZhongEtAl2024MemoryBank}
to tiered memory management \cite{PackerEtAl2023MemGPT}. More recent systems add
hierarchical storage and updating \cite{KangEtAl2025MemoryOS}, learned memory
operations \cite{YanEtAl2026MemoryR1}, and temporal graph structures with conflict
resolution \cite{BanerjeeEtAl2026APEXMEM}. Our flat, hierarchical, and graph/temporal
routes are deliberately simpler. They are controlled action variants used to test
whether memory organization creates routable differences under a fixed prompt
budget; they are not proposed as new memory architectures.

\subsection{Energy and Measurement Boundaries}

Green-AI work argues that computational cost should accompany predictive quality
\cite{SchwartzEtAl2020GreenAI,StrubellEtAl2019EnergyNLP,
HendersonEtAl2020EnergyReporting}, and inference can dominate the operational
footprint of deployed models \cite{LuccioniEtAl2024PowerHungry}. For RAG specifically,
Electro profiles retriever, retrieval-depth, and generator configurations in an
accuracy--energy landscape \cite{PanEtAl2025Electro}; a controlled software
engineering study examines energy-reduction techniques across RAG configurations
\cite{GuoEtAl2026RAGEnergy}. These studies preclude a claim that energy-aware RAG
configuration is new.

Our distinction is narrower. We pair an explicit evidence-qualified outcome with
physical T4 board-power integration during generation, disclose cross-board
non-comparability, and use the resulting trace matrix to audit whether the action
pool has a selectable quality--cost structure. The contribution is the
pre-optimization feasibility diagnosis, not broader energy coverage or a new power
instrumentation method.
