\section{HybridBench: Controlled Evidence and Memory Tasks}
\label{sec:benchmark}

\subsection{Design Objective}

\bench{} is designed for mechanism identification, not for estimating open-domain
QA performance. Its answers are opaque facts sampled independently of task class
and split. A model therefore cannot solve an evidence-required item from world
knowledge, and a task-only majority rule cannot exploit a fixed answer. The
generator is deterministic and does not call an LLM during dataset construction.

Each of the 800 scenario groups creates a project identifier, a direct-copy token,
a dataset alias, a private label, an optimizer, scheduler, seed, batch-size update,
and an authority conflict. It emits seven knowledge documents: a current optimizer
specification, old and new batch-size revisions, approved and unofficial
learning-rate records, a project-to-dataset alias, and a dataset-to-scheduler
record. It also emits three memory events: a chosen seed, a private label, and a
tombstone deleting that label. Tombstoned events are removed from active retrieval.
Every query is associated with the exact required and forbidden evidence IDs.

\subsection{Eight Task Classes}

The benchmark contains 100 scenarios in each class:

\begin{enumerate}
    \item \emph{no retrieval}: reproduce an opaque token supplied in the question;
    \item \emph{knowledge only}: recover the optimizer from an official document;
    \item \emph{memory only}: recover a previously selected seed;
    \item \emph{knowledge plus memory}: compose optimizer and seed;
    \item \emph{temporal update}: prefer the newest approved batch size;
    \item \emph{authority conflict}: prefer a signed high-authority record over a
    newer unofficial note;
    \item \emph{two-hop hybrid}: traverse project $\rightarrow$ dataset alias
    $\rightarrow$ scheduler;
    \item \emph{deleted or missing}: abstain because the relevant private fact was
    tombstoned and is not valid evidence.
\end{enumerate}

The classes separate evidence availability from evidence resolution. For example,
temporal and authority tasks require a model to select among plausible conflicting
records, whereas the deletion task requires it to avoid both retrieval and
citation of forbidden state.

\subsection{Grouped Splits and Leakage Controls}

Scenario groups are partitioned 10\%/50\%/15\%/10\%/15\% into pilot, train,
calibration, validation, and sealed test, respectively. This yields 80 pilot, 400
train, 120 calibration, 80 validation, and 120 test questions, with 15 test
questions per task class. A scenario ID appears in exactly one split. Each
task--split pair uses a distinct template family, and temporal/entity histories
remain inside the group.

The leakage audit rejects cross-split scenario overlap, template-family overlap,
exact normalized duplicates, and question-shingle Jaccard similarity at or above
0.95. Facts are randomly sampled instead of cycled by task or split. As a
construction sanity check, a task-only predictor formed from train-set answer
majorities answered 21 of the 90 evidence-requiring test items (23.33\%), below the
frozen 45\% rejection threshold. Pilot outcomes alone may remove infeasible
non-anchor routes. Router models use train outcomes; isotonic calibration uses the
calibration split; threshold and safe-route selection use validation. Test answer
fields and evidence labels remain procedurally sealed until the policy, thresholds,
and analysis plan are frozen. Because collaborators share the dataset credential,
this is a procedural seal and not a cryptographic access-control claim.

\subsection{Strict Outcome Contract}

Model output must parse as a JSON-like object with an answer, a list of exact
evidence IDs, and an abstention flag. Let $F_i$ be token F1 between the predicted
and expected answer, $R_i$ required-evidence citation recall, $P_i$ citation
precision, $A_i$ agreement with the required abstention decision, and $V_i$ an
indicator for a parseable output with no citation outside the retrieved set and no
forbidden evidence. Strict success is

\begin{equation}
\begin{aligned}
S_i=\mathbb{1}\!\big[&F_i\geq0.8 \land R_i=1 \land P_i=1 \\
                     &{}\land A_i=1 \land V_i=1\big].
\end{aligned}
\label{eq:strict-success}
\end{equation}

For tasks without required evidence, recall is one and precision is one only when
the citation set is empty. For the deleted/missing class, a correct abstention or
an explicit insufficient-evidence answer receives answer credit, but exposure of a
tombstoned ID fails the guard. The auxiliary score
$0.75F_i+0.25R_i$ is retained for diagnosis; it does not replace
Eq.~\eqref{eq:strict-success} in any primary analysis.

This contract is intentionally stricter than exact-answer accuracy. It distinguishes
three failure layers: output parsing, answer content, and evidence support. It also
prevents a fluent unsupported answer from counting as success.
