\section{Controlled Testbed and Measurement Contract}
\label{sec:testbed}

\subsection{HybridBench as a Diagnostic Testbed}

\bench{} is generated deterministically from seed 4622 without an LLM. It contains
800 independent scenario groups, 100 for each of eight task classes. Every group
defines a project, current and obsolete documents, an authority conflict, a
project--dataset--scheduler chain, personal-memory events, and a tombstone. Answers
and evidence identifiers are generated for the experiment. Their opacity minimizes
answer recovery from pretrained parametric knowledge, while exact required and
forbidden IDs make route failures observable.

The classes are: (i) copy a supplied token without retrieval; (ii) recover a fact
from authoritative knowledge; (iii) recover an active memory; (iv) compose
knowledge and memory; (v) resolve a temporal update; (vi) resolve an authority
conflict; (vii) traverse two knowledge hops; and (viii) abstain when a private fact
has been deleted or is missing. The first and last classes require no active
evidence citation. The other six collectively form the 90-question
evidence-required test stratum.

For a structurally representative temporal-update item, one scenario contains an
archived document stating batch size 8 and a newer approved document stating batch
size 16 for the same opaque project. The question asks for the current batch size;
the strict label requires answer 16 and the newer document ID. Returning 8, citing
only the archive, or citing both records fails at least one answer, recall, or
precision condition. Other classes reuse the scenario's knowledge records, memory
events, authority levels, links, or tombstone as controlled distractors. This
illustration mirrors the generator rules but is not a disclosed test item.

Scenario groups are split 10/50/15/10/15\% into pilot, train, calibration,
validation, and test: 80, 400, 120, 80, and 120 queries. A scenario appears in one
split only; task--split pairs use distinct template families. The leakage audit
rejects group overlap, template-family overlap, normalized duplicates, and
question-shingle Jaccard similarity at or above 0.95. A task-only train-majority
sanity check answered 21 of 90 evidence-required test items (23.33\%). This is a
construction diagnostic over low-cardinality task vocabularies, not a random-chance
or real-world baseline. Test labels remained procedurally sealed until the policy,
threshold, and confirmatory analysis plan were frozen; shared repository
credentials make this a procedural rather than cryptographic guarantee.

\subsection{Strict Outcome Contract}

Each generator must emit a JSON-like object containing an answer, exact evidence
IDs, and an abstention flag. Let $F_{ia}$ be answer token F1, $R_{ia}$ required-ID
citation recall, $P_{ia}$ citation precision, $A_{ia}$ correct abstention, and
$V_{ia}$ an indicator for successful parsing, no citation outside the retrieved
set, and no forbidden evidence in either retrieved or cited IDs. Strict success is

\begin{equation}
S_{ia}=\mathbb{1}\!\left[
\begin{aligned}
&F_{ia}\geq0.8 \land R_{ia}=1 \land P_{ia}=1\\
&{}\land A_{ia}=1 \land V_{ia}=1
\end{aligned}
\right].
\label{eq:strict-success}
\end{equation}

For evidence-free tasks, recall is one and precision is one only for an empty
citation set. A valid deleted/missing response must abstain or explicitly report
insufficient evidence without exposing the tombstoned identifiers. The guard is
deterministic. It checks syntax and ID membership; it does not prove semantic
entailment. We report retrieval completeness separately from citation completeness
so that evidence acquisition is not confused with evidence use.

\subsection{Composite Routes}

The predeclared catalog contains 22 actions. Pilot rules removed five non-anchor
actions, leaving 17 for the clean test matrix. Retrieval variants include BM25
\cite{RobertsonZaragoza2009BM25}, a frozen sentence-bi-encoder derived from dense
retrieval practice \cite{KarpukhinEtAl2020DPR,ReimersGurevych2019SBERT}, and bounded
hybrid retrieval using reciprocal-rank fusion \cite{CormackEtAl2009RRF}. Memory
variants use flat recency-aware retrieval, hierarchical summary-plus-event
retrieval, or graph/temporal traversal. Some actions append a deterministic support
guard. These mechanisms are experimental controls, not newly proposed retrieval or
memory algorithms.

\input{tables/frozen_parameters}

The matched panel compares each generator directly and under the same composite
grounding intervention: hybrid knowledge retrieval, graph/temporal memory, bounded
second-hop expansion, a common context budget, exact-citation prompting, and the
deterministic guard. Because several components change together, the estimand is
``composite grounding minus direct,'' not retrieval in isolation.

\input{tables/model_panel}

The checkpoints are Qwen3-0.6B and Qwen3-4B-Instruct-2507
\cite{QwenTeam2025Qwen3,QwenModelCard06,QwenModelCard4B}, Granite-4.0-1B and
Granite-4.1-3B \cite{GraniteTeam2025Granite40,GraniteTeam2026Granite41}, and
SmolLM3-3B \cite{BakouchEtAl2025SmolLM3}. All revisions, tokenizers, prompt budgets,
and FP16 loading settings are immutable. Only the 0.6B and 1B families were
available to the online controller; the 3B/4B endpoints are offline references.
This eligibility rule was frozen from the resource contract: the 0.6B and 1B
checkpoints had to coexist resident on one T4 with at least 15\% free VRAM and no
CPU or disk offload. Reference checkpoints were instead loaded and unloaded in
isolated sequential blocks. Dynamic model loading was outside the route-latency
boundary and therefore could not be treated as a zero-cost online action. We call
the resulting 11 actions the \emph{resident-eligible} or deployable pool; this is a
specific concurrency-and-latency constraint, not a claim that 3B/4B models are
undeployable in general.

\subsection{GPU-Generation-Energy Boundary}

We measure \gpuenergy{} by sampling the selected NVIDIA T4's NVML board-power
reading every 50 ms and applying trapezoidal integration

\begin{equation}
E_{ia}=\sum_{t=1}^{T-1}
\frac{P_t+P_{t+1}}{2}(\tau_{t+1}-\tau_t).
\label{eq:energy}
\end{equation}

CUDA is synchronized immediately before and after \texttt{model.generate()}.
Telemetry records physical GPU UUID, sample count, observed duration, input and
output tokens, and failure status. NVML exposes device-level power observations
\cite{NVIDIA2026NVML}; related GPU-energy instrumentation illustrates why sampling
and boundary disclosure matter \cite{YouEtAl2023Zeus}.

The reported quantity excludes CPU retrieval and embedding, memory traversal,
router computation, parsing, verification, storage, network transfer, host idle
power, cooling, and carbon. Route latency is retrieval time plus generator-call
duration; policy latency additionally includes its probe and controller components.
We make same-board paired claims where possible. Cross-board and route-major
comparisons remain descriptive because board, session, thermal, and residency
effects were not randomized away.
