\section{Discussion: From Route Catalogs to Routable Pools}
\label{sec:discussion}

\subsection{Separate Action-Space Failure from Learning Failure}

The central diagnostic is a separation of failure loci. A learned controller can
fail because its features, labels, calibration, or decision rule are inadequate.
It can also fail because its candidate set does not contain a useful conditional
choice. The first is a learning problem; the second is an action-space problem.
On the sealed resident-eligible matrix, zero routing headroom proves the latter for
strict success. The policy's universal A03 fallback adds a learning-and-selection failure,
but replacing the classifier alone cannot create successes absent from every
eligible alternative.

This distinction suggests a routing-readiness order. First validate each
model--prompt--runtime interface. Next measure individual route capability. Then
compute success unions, unique contributions, and oracle headroom. Only after
complementarity is present should one test whether decision-time features predict
which route will help. Physical cost comparison and constrained policy optimization
follow, not precede, those checks. A route catalog with many names is not necessarily
a diverse action pool in outcome space.

\subsection{A Deployment Requirement Is Not an Attainability Claim}

The frozen 80\% success floor was an operating requirement, whereas the 12.5\%
oracle ceiling is an empirical property of the eligible test matrix. Conflating the
two would make the threshold appear to be a tuning error. The correct inference is
that the pool cannot satisfy the declared requirement even with label access. A
different application may choose another requirement, but the ceiling remains
useful: it shows exactly which requirements are unattainable without changing the
action set.

At the same time, a positive oracle gap would not guarantee a successful router.
The oracle sees outcomes; a deployment policy sees query and probe features. Future
work must demonstrate that complementary successes are predictable out of sample
and that the resulting gains survive policy overhead. The audit is a necessary
filter, not a replacement for prospective evaluation.

\subsection{Grounding Should Be Conditional on Both Need and Capability}

The matched pairs explain why neither ``always retrieve'' nor ``never retrieve'' is
an adequate general policy. Direct behavior covers the supplied-token class and,
for several references, correct abstention on deleted or missing facts.
Composite-grounded endpoints add successes in several evidence-required classes
for capable generators but lose some evidence-free successes. Because retrieval,
memory, prompting, and the deterministic guard change jointly, the average
composite-grounded-minus-direct effect changes with workload composition and is not
an isolated retrieval effect.

The task-aware oracle makes the design implication concrete. For capable reference
generators, conditional grounding improves success and reduces generation energy
relative to always grounding. For Qwen3-0.6B, the composite-grounded endpoint never
adds an evidence-task success, so recognizing retrieval need alone is insufficient; the
system must also know whether the selected generator can use the retrieved
contract. This supports generator-conditional evidence policies rather than a
single model-agnostic RAG switch.

\subsection{The Interface Is Part of the Action}

Three eligible Granite-4.0-1B routes produced no parseable output. Several tiny
routes retrieved evidence but serialized citations that the exact-ID guard could
not accept. These are operational failures, not cosmetic parser details: an
evidence system needs machine-actionable outputs and predictable abstention.
However, strict syntax can reject an answer whose intent a human could recover.
Reporting parse, answer, citation, support, and strict layers separately prevents
that construct choice from being hidden.

A low-cost compatibility screen should therefore precede full route collection.
It should test chat-template application, schema adherence, termination, citation
serialization, and representative context lengths. If the integration changes,
the route specification changes; repairing it after sealed evaluation should create
a new version rather than overwrite the trace.

\subsection{Cost Claims Must Follow the Measurement Boundary}

The study supports a narrow physical statement: under the frozen same-board pairs,
the composite grounded prompt used more selected-T4 energy during generation than
the direct prompt. It does not establish total RAG energy, because retrieval,
embedding, memory traversal, routing, verification, and host overhead were excluded.
Nor does the strong energy--duration association isolate the cause of the overhead.

The conditional-oracle result also cautions against reporting only per-invocation
RAG overhead. An expensive grounded action can lower workload-average energy when
it is invoked selectively and replaces wasteful always-on grounding. Credible
deployment studies should report the invocation policy, task mixture, useful
successes, tokens, latency, and a clearly bounded energy quantity together.

\subsection{Negative Results Need Completion Without Reinterpretation}

The Stage-06 amendment permitted artifact completion while forbidding a positive
claim. That separation is important. Crashing on validation infeasibility would
have hidden the action-space diagnosis; silently relaxing the success requirement
would have contaminated the confirmatory test. A fail-closed completion state,
immutable traces, and a post-hoc analysis label allow the negative result to remain
scientifically useful without turning it into a successful router after the fact.
