\section{Threats to Validity, Reproducibility, and Ethics}
\label{sec:limitations}

\subsection{Construct and External Validity}

\bench{} is synthetic and controlled. Its generated identifiers and exact evidence
sets support mechanism diagnosis but do not estimate performance on open-domain QA,
long-document memory, conversational personalization, or production traffic. The
equal eight-class mixture is a design choice, and each test class contains only 15
queries. Model rankings and average grounding effects may change with another task
distribution, prompt, context budget, retriever, or verifier. This limitation is
especially important given evidence that synthetic context-utilization tests can
misrepresent behavior under realistic retrieval \cite{HagstromEtAl2025RealityCheck}.

Strict success is an operational conjunction. Exact-ID scoring can reject a
recoverable formatting variant, while set membership cannot prove semantic
entailment. The layered decomposition mitigates but does not remove this construct
limitation. Sensitivity at answer-F1 thresholds 0.5, 0.8, and 1.0 preserves the
ranking and effect signs of the capable grounded endpoints (Appendix~\ref{app:scenario-effects}),
but it does not test alternative citation semantics.

\subsection{Post-Hoc Diagnostics and Statistical Scope}

The action-pool oracle, routing headroom, unique-success counts, interaction
contrasts, task-aware oracle, and failure layers were specified after the
confirmatory policy failed. They use sealed-test outcomes and must not be read as
prospective policy estimates. The task-aware oracle is given the benchmark task
class, a signal that a real deployment would have to infer. Positive headroom in
the reference pool shows that complementary outcomes exist on this matrix; it does
not establish out-of-sample predictability.

Only one deterministic generation was recorded per route--query pair. Bootstrap
intervals resample scenarios and do not quantify decoding variance, repeated-run
variance, or hardware uncertainty. Exploratory intervals are not corrected for
multiple comparisons. The controller is evaluated by replaying a complete frozen
route matrix rather than by an independent prospective online deployment.

\subsection{Measurement and Hardware Validity}

The energy endpoint covers only the selected GPU board during
\texttt{model.generate()}. CPU retrieval, dense encoding, memory traversal, routing,
parsing, verification, indexing, model loading, uploads, host idle power, network,
cooling, and storage are outside the boundary. No idle-power subtraction,
whole-system instrumentation, carbon conversion, or token-normalized causal model
is reported. Consequently, the work does not measure whole-system energy and does
not measure carbon emissions.

Four T4 boards were used, execution was route-major, and routes were not randomized
or interleaved. Board, session, temperature, and residency can confound cross-lane
or cross-model comparisons. Four matched effects are same-board; the
Granite-4.0-1B pair is cross-board. Input and output tokens also differ, so this is
not an intrinsic architecture-efficiency leaderboard.

\subsection{Model, Protocol, and Robustness Limits}

Different model families use different tokenizers and chat templates. The
Granite-4.0-1B integration failure is specific to the frozen
model--prompt--runtime triple. It cannot support a general capability claim about
the checkpoint. Five non-anchor actions were pilot-pruned. The 3B/4B references
were excluded because they were run sequentially, whereas eligible models had to
coexist on one T4 with 15\% free VRAM and no offload; model-loading time was not in
the route-latency boundary. This resident-set constraint is defensible for the
frozen controller but not universal. Dynamic loading, another accelerator, or a
different eligible set would induce another routing problem.

The threshold-completion amendment occurred after validation infeasibility was
known but before test labels were accessed. It is disclosed, preserved in the
policy artifact, and prohibits a positive router claim, but it remains a protocol
deviation. The test seal was procedural because collaborators shared repository
access. The robustness matrix covers only three anchors and four synthetic
corruptions; its all-zero selected-policy outcome cannot demonstrate a defense.

\subsection{Reproducibility and Ethics}

The release contains 2,040 clean and 1,440 robustness traces with complete declared
generation-window telemetry, frozen specifications, checksums, route cards,
analysis code, and the amended policy. Artifacts were consolidated without deleting
worker branches, restored into a fresh directory, and hash-verified before release.
This supports audit and exact re-analysis, although reproducibility on a different
T4 may not reproduce the same power readings.

The generated benchmark contains no personal information; memory records and
deletion events are synthetic. No external sponsor influenced the study. Because
the work neither measures whole-system energy nor converts electricity to emissions,
it makes no claim about avoided carbon or environmental impact. If the dataset
repository is private during review, an anonymous checksum-preserving archive is
required for reviewers.
