\section{Reproducibility and Artifact Manifest}
\label{app:reproducibility}

\subsection{Frozen Counts and Identifiers}

The release identifier is \modelid{e2am-memrag-v3r1}; the execution-spec SHA-256
is \artifactid{1c8f29fd\allowbreak 250b87d3\allowbreak 546c6ff3\allowbreak
d128dc3f\allowbreak e6600bc7\allowbreak 98c3c0b0\allowbreak b8c98e0b\allowbreak
95c76cfc}.
The visible Hugging Face release commit is
\artifactid{0b2405d9\allowbreak cca43fd0\allowbreak 4e35f792\allowbreak
fdc46644\allowbreak 05154fc6}; the paper-release branch commit is
\artifactid{00fa353f\allowbreak 273f3a4b\allowbreak 3d57a0b9\allowbreak
98301c85\allowbreak a1bc098b}. Eleven Stage-09 artifacts totaling
11,528,142 bytes passed byte and SHA-256 verification.

The benchmark contains 5,600 documents and 2,400 memory events across 800 scenario
groups. After tombstone processing, one selected-seed memory per scenario remains
active. The clean release contains 17 routes, 120 query IDs, and 2,040 rows; the
robustness release contains three routes, four conditions, 120 query IDs, and 1,440
rows.

\subsection{Rebuild Procedure}

The repository script \path{scripts/build_manuscript_assets.py} reads the
checksum-verified release, reconstructs the frozen deterministic test metadata, and
regenerates manuscript CSVs, tables, and vector figures. This includes pool oracles,
headroom, task-aware choices, failure layers, interaction contrasts, and threshold
sensitivity; it never invokes a model. \path{scripts/validate_manuscript.py} checks numeric claims,
bibliography keys, references, measurement-boundary language, artifact existence,
and protocol-amendment disclosure. The complete source is compiled with Tectonic
0.16.9 using \path{paper/manuscript/main.tex}; the same sources are compatible
with Overleaf/pdfLaTeX.

\subsection{Availability}

Code and paper sources are hosted at
\url{https://github.com/Shanmuk4622/E2AM-MemRAG}. Frozen traces reside in the
Hugging Face dataset \path{Shanmuk4622/E2AM-MemRAG-Traces}. Repository visibility
must be checked at submission time. If the trace repository is not public, the
authors should provide a checksum-identical anonymous archive or grant reviewer
access rather than claiming unrestricted availability.

\input{tables/trace_integrity}

\subsection{Author Contribution and Conflicts}

Shanmukesh Bonala conceived the study, implemented the benchmark and pipeline,
executed and audited the experiments, analyzed the data, and wrote the manuscript.
The author declares no competing interests and no external funding for this study.
