\section{Scoring and Router Contract}
\label{app:scoring}

\subsection{Token and Citation Metrics}

Let $n_t^{\hat y}$ and $n_t^y$ denote predicted and target token counts. Answer
precision, recall, and F1 are

\begin{align}
P_{\mathrm{ans}} &=
\frac{\sum_t\min(n_t^{\hat y},n_t^y)}{|T_{\hat y}|}, \\
R_{\mathrm{ans}} &=
\frac{\sum_t\min(n_t^{\hat y},n_t^y)}{|T_y|}, \\
F_1 &= \frac{2P_{\mathrm{ans}}R_{\mathrm{ans}}}
{P_{\mathrm{ans}}+R_{\mathrm{ans}}}.
\end{align}

For required IDs $R_q$ and cited IDs $C_{qr}$,

\begin{equation}
R_{\mathrm{cite}}=\frac{|C_{qr}\cap R_q|}{|R_q|},\qquad
P_{\mathrm{cite}}=\frac{|C_{qr}\cap R_q|}{|C_{qr}|}.
\end{equation}

Recall is one when no evidence is required. Precision for an empty citation set is
one only when no evidence is required. Strict success additionally requires
$C_{qr}\subseteq G_{qr}$ for retrieved IDs $G_{qr}$ and
$F_q\cap(C_{qr}\cup G_{qr})=\varnothing$ for forbidden IDs $F_q$.

\subsection{Router Features and Hyperparameters}

The eight query-only features are token count, character count, digit count,
entity-code count, temporal-term count, conflict-term count, memory-term count, and
multi-hop-term count. The eight probe features are document top score, document
score gap, document count, memory top score, memory score gap, memory count,
maximum authority, and authority range.

Each bootstrap model uses histogram gradient boosting with learning rate 0.06,
180 iterations, at most 15 leaves, and $L_2=1$. Success is calibrated by isotonic
regression; energy and latency use 0.90-quantile loss on log outcomes. Bootstrap
seeds are 4622, 1701, 31415, 27182, and 65537.

\subsection{Validation Amendment Record}

The frozen policy records the following non-negotiable fields:

\begin{itemize}
    \item amendment ID:
    \modelid{stage06-threshold-completion-separation-v1};
    \item timing: after validation, before test access;
    \item validation feasible: false;
    \item selected threshold: $\tau=1.0$;
    \item selection mode:
    \modelid{fail-closed-tau-1.0-validation-infeasible};
    \item positive hypothesis claim permitted: false.
\end{itemize}

Every tested threshold from 0.60 to 1.00 had 8.75\% validation success, 100\%
execution coverage, and 18.75\% abstention. The frozen policy file has SHA-256
\artifactid{fda2bda0\allowbreak a7152271\allowbreak 62ceead0\allowbreak
ff032f22\allowbreak 28999f6d\allowbreak c9f4bb22\allowbreak 890ec23a\allowbreak
4acdab14}
in the Stage-06 manifest.
